Guided Proofreading of Automatic Segmentations for Connectomics

### 2016-11-15 paper/results.tex

@@

We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.

\subsection{Selection Oracle}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/gpusers.pdf}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.24\textwidth}
        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
%    \begin{subfigure}[b]{0.15\textwidth}
%        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
%        \caption{A mouse}
%        \label{fig:mouse}
%    \end{subfigure}
    \caption{Pictures of animals}\label{fig:animals}
\end{figure*}
\begin{figure}
    \centering
    \begin{subfigure}[b]{0.48\linewidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.49\linewidth}
        \includegraphics[width=\textwidth]{gfx/gpusers.pdf}
        \caption{A tiger}
        \label{fig:tiger}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
%    \begin{subfigure}[b]{0.15\textwidth}
%        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
%        \caption{A mouse}
%        \label{fig:mouse}
%    \end{subfigure}
    \caption{Pictures of animals}\label{fig:animals}
\end{figure}

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\linewidth}
        \includegraphics[width=\textwidth]{gfx/gpauto.pdf}
        \caption{A gull}
        \label{fig:gull}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)

    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.49\linewidth}
        \includegraphics[width=\textwidth]{gfx/fc_fp_ac4.pdf}
        \caption{A mouse}
        \label{fig:mouse}
    \end{subfigure}
    \caption{Pictures of animals}\label{fig:animals}
\end{figure}

>>>>

\begin{figure*}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4trails.pdf}
\end{center}
  \vspace{-4mm}
   \caption{Performance comparison of focused proofreading by Plaza and our guided proofreading methods on the AC4 subvolume. All measurements are reported as median VI, the lower the better. We compare different approaches of accepting or rejecting corrections for each method: automatic selection with threshold (indicated by the red line), forced choice by ten novice users, forced choice by two domain experts, and the selection oracle. In all cases, guided proofreading yields better results with less corrections.}
\label{fig:ac4trails}
\end{figure*}

\begin{figure}[t]
\begin{center}
\includegraphics[width=\linewidth]{gfx/ac4boxplot.pdf}
\end{center}
  \vspace{-4mm}
   \caption{VI distributions of proofreading output across ten slices of the AC4 subvolume. The different decision approaches yield different proofreading performances.}
\label{fig:ac4trails}
\end{figure}

@@

%We measure the performance of proofreading quantitatively by comparing VI scores of segmentations against ground truth labelings. Lower VI scores indicate less distance to the ground truth and a better segmentation. For all experiments, we report the VI score of the initial segmentation followed by the VI score of the proofreading output.

\subsection{Selection Oracle}
Accepting and rejecting proofreading corrections with the selection oracle yields the best performance on all datasets. This is not surprising since all detected merge and split are corrected if they are good corrections.

@@
